---
title: "penguins-assemble"
author: "Alison Hill"
date: "6/23/2021"
output: html_document
---

```{r setup, include=FALSE, purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(tidyverse)
library(palmerpenguins)
```

---
<!--control panel-->

## Wrangle

```{r}
source("wrangle.R", local = knitr::knit_global())
```

```{r}
shrimpiest_penguins 
```

Julie: after you type this bit up, run interactive, then knit

Julie: knit is ugly b/c of messages

Alison: turn off messages for package loading chunk only, then reknit

Alison: can suggest that you echo false and pipe knitr::kable

```{r echo=FALSE}
shrimpiest_penguins %>% 
  knitr::kable()
```

Julie: reknits, tada

## Plot

```{r}
source("plot.R", local = knitr::knit_global())
```

```{r}
ggflipper_body
```

Alison: this motivates a setup chunk, let's add warning FALSE. you could also do message false there to in the setup to clean up your output

Julie: edit setup chunk to look like, then reknit:

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.path = "penguins-figs/")
```

Julie: reknit, oh that is awesome, can you make the name better?

Alison: let's name that code chunk that makes the figure and see

Julie:
```{r scatterplot-species}
ggflipper_body
```

reknit, watch as the figure populates to the new folder 
also, can point out new thing in drop-down code navigator

---
<!--read chunk-->

## Read chunk

Julie: Ok so Alison this is great. If I have a full R script, I can source it.

What if I want to organize

Alison: let's open up penguins_plots.R and add:

## ---- penguin-pairs ----
## ---- iris-pairs ----

Now you can:

+ collapse this code so you can find what you are looking for faster. 
+ You can also use the drop-down code navigator

```{r}
knitr::read_chunk("penguins_plots.R")
```

Alison: 

```{r include = FALSE}
knitr::read_chunk("penguins_plots.R")
```

```{r penguin-pairs}
```


```{r iris-pairs}
```

---
<!--knit child-->
# Knit Child

NOW I’ve got these other small .Rmds. instead of R scripts

```{r, child="penguins-background.Rmd"}

```

A new way to reuse your code so when you're developing content for diff audiences: Might always want this in your grant application, or your samples. 

Alison: Conditionally including text/some parts of your story. 

There's a lot of other ways to get your code from one file into another, but here we're also doing it nicely with text. we can also do it with code: 

```{r, child="penguins-simpson.Rmd"}

```

---
<!--purl-->

Finale: in console

```{r}
knitr::purl("penguins-assemble.Rmd")
```

Then use purl=FALSE as a chunk option to leave individual ones out of the script
